Paper 1 Analysis

### 2015-11-12 Articles/Article_EcolEcon_2015/Paper1/Paper1-lambda-alpha.Rnw
Moved OMTable.

@@

<<OMTable, results="asis">>=
    # Make the LaTeX table
    myXTable(OMTable, caption="Solow residual~($\\lambda$) and SSE for $(kl)e$ models.",
           label=paste0("tab:", opts_current$get("label")), 
           digits=c(1,1,1,1,1,1, 4, 2, 3))
@

>>>>

<<OMTable, results="asis">>=
  # Make the LaTeX table
  myXTable(OMTable, 
           caption="Solow residual~($\\lambda$) and sum of squared errors~(SSE) for $(kl)e$ models that reject the cost share principle. 
             $\\lambda / \\lambda_{Ref.}$ is the ratio of Solow residual relative to the reference (exponential-only) model.
             ``UA'' and ``QA'' indicate unadjusted and quality-adjusted factors of production, respectively.",
           label=paste0("tab:", opts_current$get("label")), 
           digits=c(1,1,1,1,1,1, 4, 2, 3))
@

@@
